Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
abstract

%\section{Running Example}
%\label{running-example}
\section{Common Vocabularies in SBE Sciences}
\label{rdf-representation}
\tb{Ich habe Beschreibungen von XKOS und DCAT noch ganz am Ende eingeführt (jeweils nur 1 Satz)}
%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.

@@

%\textbf{Metadata on Person-Level Data.}
For more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}. 
%published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
Where data collection is cyclic, data sets may be released as \emph{series}, 
where each cycle produces one or more data sets. 
%\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. 
%This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables 
(e.g., \emph{Education at pre-school}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}})
%(2) Education at compulsory school,
%(3) Child care at centre-based services,
%(4) Child care at day-care centre,
%(5) Child care by a professional child-minder, and
%(6) Child care by grand-parents, household members, relatives, friends, neighbours.
for which detailed metadata is given 
%(definitions, descriptions, theoretical concepts, questions variables are based on, code lists, frequencies, descriptive statistics, countries, year of data collection, and classifications) 
(e.g., code lists)
enabling researchers to replicate the results shown in aggregated data tables.
The \emph{DDI-RDF Discovery Vocabulary (Disco)} is a vocabulary to represent metadata on person-level data in RDF.
The series (\emph{disco:StudyGroup}) \emph{EU-SILC} contains one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
\emph{dcterms:spatial} points to the countries for which the data has been collected.
The study \emph{EU-SILC 2011} contains eight person-level data sets (\emph{disco:LogicalDataSet})
including person-level variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
%Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
%One common research question is ,e.g., the comparison of variables like 
%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).

@@

2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
\emph{QB} violations are almost only raised by \emph{complex constraints}, and 
nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
For well-established vocabularies, \emph{vocabulary constraints} are almost completely satisfied\footnote{e.g. only 1.777 \emph{QB} violations} which indicates good data quality according to formal specifications of vocabularies.
%This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
For newly defined vocabularies, however, 2/3 of all violations are raised by \emph{vocabulary constraints}
which indicates bad data quality with regard to the formal specifications of vocabularies.

@@

\begin{hyp}
A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible in existing constraint languages which confirms the necessity to provide suitable constraint languages.
\end{hyp} 
In general, \emph{vocabulary} and \emph{simple constraints} are easily, concisely, and intuitively expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}). 
This is not the case, however, for \emph{complex constraints} which in most cases are still only expressible by plain \emph{SPARQL}. 
As almost 1/2 of all violations are caused by \emph{complex constraints}, 
data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{complex constraints} in an easy, concise, and intuitive way.
%Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
1/2 of all constraints are \emph{error constraints} and
10\% of all constraints are \emph{warning constraints}.
\emph{Informational constraints} caused 1/3 and
\emph{warning constraints} 2/3 of all violations.
As the percentage of severe violations is very low for all vocabularies,
data quality is high with regard to the severity level of constraints.

@@

\tb{
die vokabular-beschreibungen klarer strukturieren. du nutzt plötzlich disco elemente, disco wird überhaupt nicht vernünftig eingeführt, obwohl es später untersucht wird
alles, was nicht der aussage des papers (neuer titel, btw) dient, solltest du weglassen
klare, einfache struktur: 1. grundidee (constraints identifizieren, validieren auf datensets, zu belastbaren aussagen kommen für die weitere entwicklung von constraint languages)
2. vorstellung der untersuchten vokabulare
3. beschreiben, wo die constraints herkommen, bzw. wie die generiert wurden. dabei auch auf die klassifikation eingehen, aber nur im hinblick auf die spätere auswertung, nicht als main contribution des papers
4. evaluation mit beschreibung der datasets in setup (das les ich mir gleich mal durch, das hast du ja schon neu geschrieben)
ja, und dann prägnante conclusion mit zusammenfassung der hypothesen, der bedutung für die weitere entwicklung von CLs und natürlich future work
}

>>>>

%\section{Running Example}
%\label{running-example}
\section{Common Vocabularies in SBE Sciences}
\label{rdf-representation}
\tb{Ich habe Beschreibungen von XKOS und DCAT noch ganz am Ende eingeführt (jeweils nur 1 Satz)}\tb{die vokabular-beschreibungen klarer strukturieren}
%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.

@@

%\textbf{Metadata on Person-Level Data.}
For more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}. 
%published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
Where data collection is cyclic, data sets may be released as \emph{series}, 
where each cycle produces one or more data sets. 
%\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. 
%This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
%\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
%Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables 
(e.g., \emph{Education at pre-school}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}})
%(2) Education at compulsory school,
%(3) Child care at centre-based services,
%(4) Child care at day-care centre,
%(5) Child care by a professional child-minder, and
%(6) Child care by grand-parents, household members, relatives, friends, neighbours.
for which detailed metadata is given 
%(definitions, descriptions, theoretical concepts, questions variables are based on, code lists, frequencies, descriptive statistics, countries, year of data collection, and classifications) 
(e.g., code lists)
enabling researchers to replicate the results shown in aggregated data tables.
The \emph{DDI-RDF Discovery Vocabulary (Disco)} is a vocabulary to represent metadata on person-level data in RDF.
The series (\emph{disco:StudyGroup}) \emph{EU-SILC} contains one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
\emph{dcterms:spatial} points to the countries for which the data has been collected.
The study \emph{EU-SILC 2011} contains eight person-level data sets (\emph{disco:LogicalDataSet})
including person-level variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
%Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
%One common research question is ,e.g., the comparison of variables like 
%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).

@@

\tb{je nach hypothese spezifische aufgaben um die hypothese zu beweisen}
2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
\emph{QB} violations are almost only raised by \emph{complex constraints}, and 
nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
For well-established vocabularies, \emph{vocabulary constraints} are almost completely satisfied\footnote{e.g. only 1.777 \emph{QB} violations} which indicates good data quality according to formal specifications of vocabularies.
%This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
For newly defined vocabularies, however, 2/3 of all violations are raised by \emph{vocabulary constraints}
which indicates bad data quality with regard to the formal specifications of vocabularies.

@@

\begin{hyp}
A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible in existing constraint languages which confirms the necessity to provide suitable constraint languages.
\end{hyp}

In general, \emph{vocabulary} and \emph{simple constraints} are easily, concisely, and intuitively expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}). 
This is not the case, however, for \emph{complex constraints} which in most cases are still only expressible by plain \emph{SPARQL}. 
As almost 1/2 of all violations are caused by \emph{complex constraints}, 
data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{complex constraints} in an easy, concise, and intuitive way.
%Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
1/2 of all constraints are \emph{error constraints} and
10\% of all constraints are \emph{warning constraints}.
\emph{Informational constraints} caused 1/3 and
\emph{warning constraints} 2/3 of all violations.
As the percentage of severe violations is very low for all vocabularies,
data quality is high with regard to the severity level of constraints.

@@

\tb{ 
klare, einfache struktur: 1. grundidee (constraints identifizieren, validieren auf datensets, zu belastbaren aussagen kommen für die weitere entwicklung von constraint languages)
2. vorstellung der untersuchten vokabulare
3. beschreiben, wo die constraints herkommen, bzw. wie die generiert wurden. dabei auch auf die klassifikation eingehen, aber nur im hinblick auf die spätere auswertung, nicht als main contribution des papers
4. evaluation mit beschreibung der datasets in setup (das les ich mir gleich mal durch, das hast du ja schon neu geschrieben)
ja, und dann prägnante conclusion mit zusammenfassung der hypothesen, der bedutung für die weitere entwicklung von CLs und natürlich future work
}
